On Secure Delegation of SampBQP with a Classical Client

### 2020-03-18 qpip0.tex
Updates from Overleaf

\begin{definition}[quantum computationally indistinguishable]
\hannote{move later}
Let  $D_1$ and $D_2$ be distributions over $n$-bit string.  We say $D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable if for all quantum circuit $A$ of size $\poly(n)$, $$\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \leq \eps,$$  where $A(D_1)$ means $A$ takes \emph{one} sample from $D_1$ as part of its input. We also denote this as 
$$ D_1 \approx_{q,\eps} D_2$$
\end{definition}
%Let $O^{D_1}$ and $O^{D_2}$ be oracles giving samples from $D_1$ and $D_2$.

@@

\begin{rmk}
If $\norm{D_1-D_2}_1\leq \eps$, $D_1$ and $D_2$ are $\eps$-Q-computationally indistinguishable.
\end{rmk}

\begin{lem}[triangle inequality for computational distance]
Let $D_1$, $D_2$ be two distributions such that $D_1=D_3+D_4$ and $D_2=D_5+D_6$, where $D_3$, $D_4$, $D_5$, and $D_6$ are subnormalized distributions.

If 
\begin{align}
    D_1 &\approx_{q,\eps} D_2 \\
    D_4 &\approx_{q,\eps'} D_6, 
\end{align}
then 
\begin{align}
    D_3 \approx_{q,\eps+\eps'} D_5
\end{align}
\end{lem}
\begin{proof}

@@

@@

\begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ that is $\negl(n)$-Q-computationally indistinguishable from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

@@

We have 
\begin{align}
    \tr|z-z_{good}| =& \tr\L|\frac{1}{m}\sum_i (z_i-z_{good,i})\R| \nn \\
    \leq&  \frac{1}{m}\sum_i\tr| (z_i-z_{good,i})| \nn \\
    \leq&  \frac{1}{m}\sum_i\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)\R] \nn \\%%%%%%%%
    \leq&  \frac{1}{m}+ 2\frac{1}{\sqrt m}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R) \nn \\ %%%%%
    =&O\L( \frac{1}{\sqrt m}+\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)
\end{align}

@@

For every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp} and $i\in [m]$, consider the following prover strategy for Protocol~\ref{proto:urmila4}: on the second round, the prover tries to run $U_0$ by taking the verifier's input as $i$-th copy of protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself. The prover then \hannote{picks a uniformly random $\gamma$ ?}  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$. If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and run $U_{trivial,0}$ described  in  fact ??? instead. On the fourth round, if the prover had generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$. otherwise he run $U_{trivial}$    described  in  fact ???.

By

@@

\hannote{below are unused old fragments}

>>>>

\begin{definition}[quantum computationally indistinguishable]
\hannote{move later}
Let  $D_1$ and $D_2$ be distributions over $n$-bit string.  We say $D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable if for all quantum circuit $A$ of size $\poly(n)$, $$\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \leq \eps,$$  where $A(D_1)$ means $A$ takes \emph{one} sample from $D_1$ as part of its input. We also denote "$D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable" as 
$$ \norm{D_1 - D_2}_q \leq \eps.$$
And "$D_1$ and $D_2$  are not $\eps$-Q-computationally indistinguishable" as 
$$ \norm{D_1 - D_2}_q > \eps.$$
\end{definition}
%Let $O^{D_1}$ and $O^{D_2}$ be oracles giving samples from $D_1$ and $D_2$.

@@

\begin{rmk}\label{rmk:trace-to-comp}
If $\norm{D_1-D_2}_1\leq \eps$, $D_1$ and $D_2$ are $\eps$-Q-computationally indistinguishable.
\end{rmk}

\begin{lem}[triangle inequality for computational distance] \label{lem:computational-triangle0}
    Let $D_1$, $D_2$, and $D_3$ be three distributions such that 
    \begin{align}
        \norm{D_1 -D_2}_q &\leq \eps \\ 
        \norm{D_2 -D_3}_q &\leq \eps'. 
    \end{align}
    We have 
    \begin{align}
        \norm{D_1 -D_3}_q &\leq \eps+\eps'
    \end{align}
\end{lem}
\begin{proof}
For all quantum circuits $A$ with size $\poly(n)$, we have 
\begin{align}
    \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]} \leq& \eps \\
    \norm{\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \leq& \eps',  
\end{align}
so 
\begin{align}
    &\norm{\Pr[A({D_1})=1]-\Pr[A({D_3})=1]} \nn \\
    =& \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]+\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \nn \\
    \leq&  \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]} +\norm{\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \nn \\
    =& \eps +\eps' \nn
\end{align}

@@

\begin{lem}[another triangle inequality for computational distance]\label{lem:computational-triangle}
Let $D_1$, $D_2$ be two distributions such that $D_1=D_3+D_4$ and $D_2=D_5+D_6$, where $D_3$, $D_4$, $D_5$, and $D_6$ are subnormalized distributions.

If 
\begin{align}
    &\norm{D_1 - D_2}_q \leq \eps   \\ 
    &\norm{D_4 - D_6}_q \leq \eps',  
\end{align}
then 
\begin{align}
   \norm{ D_3 - D_5}_q \leq \eps+\eps' 
\end{align}
\end{lem}
% \begin{align}
%     D_1 &\approx_{q,\eps} D_2 \\
%     D_4 &\approx_{q,\eps'} D_6, 
% \end{align}
% then 
% \begin{align}
%     D_3 \approx_{q,\eps+\eps'} D_5
% \end{align}
\begin{proof}
% Since
% $$\norm{D_4 - D_6}_q \leq \eps',$$
% there exist

We prove by contradiction. Suppose that
$$\norm{ D_3 - D_5}_q > \eps+\eps',$$
then there exist a quantum circuit $A$ of size $poly(n)$ such that 
$$\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| > \eps+\eps'.$$
Since $$\norm{D_4 - D_6}_q \leq \eps'$$, we know that 
$$\L\|\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \leq \eps'.$$
Since $D_1=D_3+D_4$ and $D_2=D_5+D_6$, we have that
$$ \Pr[A({D_1})=1]= \Pr[A({D_3})=1]+ \Pr[A({D_4})=1]$$ 
$$ \Pr[A({D_2})=1]= \Pr[A({D_5})=1]+ \Pr[A({D_6})=1].$$ 
So 
\begin{align}
    &\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \nn \\
    =&   \L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1] +\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \nn \\
    \geq  &\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| - \L\|\Pr[A({D_6})=1]-\Pr[A({D_4})=1]  \R\|  \nn \\
     > &\eps 
\end{align}
This contradicts with the assumption that $\norm{D_1 - D_2}_q \leq \eps $.
\end{proof}

@@

\begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

@@

We have 
\begin{align} \label{eq:z-z-good}
    \tr|z-z_{good}| =& \tr\L|\frac{1}{m}\sum_i (z_i-z_{good,i})\R| \nn \\
    \leq&  \frac{1}{m}\sum_i\tr| (z_i-z_{good,i})| \nn \\
    \leq&  \frac{1}{m}\sum_i\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)\R] \nn \\%%%%%%%%
    \leq&  \frac{1}{m}+ 2\frac{1}{\sqrt m}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R) \nn \\ %%%%%
    =&O\L( \frac{1}{\sqrt m}+\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)
\end{align}

@@

For every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for Protocol~\ref{proto:urmila4}: on the second round, the prover start with picking a uniformaly random $i\in [m]$. The prover then tries to run $U_0$ by taking the verifier's input as $i$-th copy of protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself. The prover then \hannote{picks a uniformly random $\gamma$ ?}  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$. If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and run $U_{trivial,0}$ described  in  Lemma~\ref{lem:trivial-4-round-strategy} instead. This is possible because all the inputs are classical. On the fourth round, if the prover had generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$, where $\ext_i$ is specified in property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}. otherwise he continues to run the strategy of Lemma~\ref{lem:trivial-4-round-strategy}. We denote the random variable the verifier would get on the testing round as $z_{construct}$.

By Lemma~\ref{lem:trivial-4-round-strategy} and property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$. Therefore by Lemma~\ref{lem:urmila-binding}, there exist a $\rho_{composite}$ such that

\begin{align}
    \norm{z_{composite} - M_{XZ}(\rho_{composite},h) }_q \leq \negl(n) 
\end{align}

By Lemma~\ref{lem:trivial-4-round-strategy} and Lemma~\ref{lem:urmila-binding}, there exist a $\rho_{trivial}$ such that

\begin{align}
    \norm{z_{trivial} - M_{XZ}(\rho_{trivial},h) }_q \leq \negl(n), 
\end{align}
where $z_{trivial}$ is the random variable one get by running the strategy of Lemma~\ref{lem:trivial-4-round-strategy}, normalized by the probability that the trivial strategy is chosen in the composite strategy. $\rho_{trivial}$ is normalized by the same probability.

Note that when $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$ succeeded, the corresponding output would be $z_{good}$. Therefore $z_{composite}=z_{good}+z_{trivial}$, and by Lemma~\ref{lem:computational-triangle},

\begin{align} \label{eq:z-good-rho}
    \norm{z_{good} - M_{XZ}(\rho_{good},h) }_q \leq \negl(n), 
\end{align}
where $\rho_{good} \defeq \rho_{composite}-\rho_{trivial}$.

Recall that by Eq~\ref{eq:z-z-good} we have
\begin{align} \label{eq:z-z-good2}
    \norm{z-z_{good}}_1 \leq \eps
\end{align}
if we pick $m,T,\gamma_0=???$ \hannote{tune eps}

Also note that by theorem~\ref{QPIP1thm}, 
\begin{align} \label{eq:rho-c}
    \norm{M_{XZ}(\rho_{good},h) -p_{good} C(x)}_1 \leq \eps, 
\end{align}
where $p_{good} = \tr \rho_{good}$.

Putting together Equation~\ref{eq:z-z-good2}\ref{eq:z-good-rho}\ref{eq:rho-c}, and Remark~\ref{rmk:trace-to-comp} and Lemma~\ref{lem:computational-triangle0}, we have  
\begin{align}
    \norm{z- p_{good}C(x)}_q \leq 2\eps +\negl{n}
\end{align}

\hannote{below are unused old fragments}
===

@@
